\section{Functional Requirements}
\label{sect:functional_requirements}

\subsection{Level 1 Requirements}
\label{sect:level_1_requirements}

Listed below are the level 1 functional requirements which detail functions and features that will be covered in the prototypes interface due in December 2019 and will be fully implemented (from an execution point of view).

\begin{enumerate}[itemsep=1mm, parsep=0pt]
    \item {The system shall provide the end-user access to PyBank through an interactive graphical user interface.}
    \item {The system shall provide an application window for creating a new account or signing into an existing account using text-entry boxes and buttons.}
    \item {The system shall provide username and password checking to verify an end-user's login credentials.}
    \item {The system shall provide the end-user with error dialog windows as feedback for rejected actions.}
    \item {The system shall provide an account overview for an existing user account in the main application window.}
    \item {The system shall provide the end-user with dialog windows as feedback for successful transactions (deposit/withdraw).}
    \item {The system shall request end-user verification before proceeding with any transaction.}
    \item {The system shall provide the ability to request a checking account from the main application window.}
    \item {The system shall provide the ability to view an end-user's checking account from the account overview main application window once signed in.}
    \item {The system shall provide the ability to request a savings account from the main application window.}
    \item {The system shall provide the ability to view an end-user's savings account from the account overview main application window once signed in.}
    \item {The system shall provide various menu options via a menu bar at the top of the main application window.}
    \item {The system shall provide visualizations related to the end-user's checking and spending accounts.}
    \item {The system shall provide the end-user with buttons in their checking and/or savings account(s) to perform actions for depositing and withdrawing money from PyBank.}
\end{enumerate}

\newpage

\subsection{Level 2 Requirements}
\label{sect:level_2_requirements}

Listed below are the level 2 functional requirements which detail functions and features that will be covered in the prototype's interface due in December 2019 but will not be fully implemented.

\begin{enumerate}[itemsep=1mm, parsep=0pt]
    \item {The system shall provide the ability to transfer funds to other PyBank customers.}
    \item {The system shall provide a `switch theme' menu option.}
    \item {The system shall provide the ability to request a credit card account.}
    \item {The system shall provide the ability to view an end-user's credit card account from the account overview main application window once signed in.}
    \item {The system shall provide a `help' menu option.}
\end{enumerate}

\subsection{Level 3 Requirements}
\label{sect:level_3_requirements}

Listed below are the level 3 functional requirements which detail functions and features that will not be covered in the prototype due in December 2019 but would be useful in a possible continuation of the project beyond the time frame of this course.

\begin{enumerate}[itemsep=1mm, parsep=0pt]
    \item {The system shall use modern encryption techniques to protect the account creation and sign-in processes.}
    \item {The system shall provide advanced visualizations and using statistical techniques.}
    \item {The system shall add additional options for customizing the applications interface.}
    \item {The system shall provide predictive models based on spending trends.}
    \item {The system shall provide the end-user with detailed reports related to their existing accounts.}
\end{enumerate}

% EOF